\subsection{Presentation}

A naive approach to the exact algorithm for solving the MEWC problem works by
exploring all potential cliques in the graph and selecting the clique with the
maximum weight. To do this, the algorithm uses a recursive function to explore
all possible subsets of V. For each subset, the algorithm computes the weight of
the clique formed by the vertices in the subset. If the weight is greater than the
current maximum weight, the clique is selected as the current maximum. This
process is repeated until all possible cliques have been explored, at which point
the algorithm returns the clique the the maximum weight.
\newline \newline
The time complexity of this approach is $\mathcal{O}(n^2\times2^n)$, where $n$
is the number of vertices in the graph. This is due to the fact that there are
$2^n$ possible subsets of V, and the algorithm must compute the weight of the clique,
which by itself has a complexity of $\mathcal{O}(n^2)$ because there are at most
$\frac{n(n-1)}{2}$ edges in a complete graph, and compare it to the current
maximum weight. Therefore, the algorithm is only feasible for small-scale graphs.
\newline \newline
However we could only look at the maximal cliques of the graph, which would
reduce the number of subsets to explore. A clique is maximal if it is not a
subgraph of any other clique. To find all maximal cliques in a graph, we can use
the \textbf{Bron-Kerbosch} algorithm\cite{finding-all-cliques-of-an-undirected-graph}.
This algorithm has a time complexity of $\mathcal{O}(\sqrt[3]{3}^n)$, where $n$
is the number of vertices in the graph. This is optimal, as it has been proven by
J. W. Moon \& L. Moser in 1965\cite{on-cliques-in-graphs} that there are at most
$\sqrt[3]{3}^n$ maximal cliques in any n-vertex graph and $\sqrt[3]{3} \approx 1.44 < 2$.
\newline \newline
We can use the Bron-Kerbosch algorithm to find all maximal cliques in the graph,
and then compute the weight of each clique. This approach has a time complexity of
$\mathcal{O}(n^2\sqrt[3]{3}^n)$, which is much better than the previous
approach. However, this algorithm is still not feasible for large-scale graphs.