% ----- Introduction -----

\section{Introduction}

\subsection{Presentation}

\textbf{Graph theory} is a branch of mathematics that deals with the study of graphs,
which are mathematical structures used to model pairwise relationships between
objects. Graphs consist of vertices (also called nodes) that are connected by
edges. The edges can be either directed (one-way) or undirected (two-way) and can
also have a weight. \newline

\textbf{The Maximum Edge Weight Clique} (MEWC) problem is an optimization problem
in graph theory that asks for the clique (a subset of vertices, all adjacent to
one another) with the maximum total weight in an edge-weighted undirected graph.
In the MEWC problem, each edge has a weight, and the weight of a clique is the
sum of the weights of its edges. The goal is to find a clique with the maximum
possible weight. \newline

Now, the MEWC problem is \textbf{NP-hard}, which means that it is not possible
to find an efficient algorithm to solve it in polynomial time or that this problem
is at least as hard as the hardest problems in NP. It is also the generalization
of the Maximum Clique Problem (MCP), which is the special case where all edges
have the same weight. \newline

\begin{minipage}{0.5\textwidth}
    For example, the following graph $G=(V,E)$ has for its set of vertices
    $V=\{1,2,3,4,5,6\}$ and for its set of edges
    $E=\{(1,2),(1,5),(2,3),(2,5),(3,4),(4,5),(4,6)\}$.
    As we can see, the red edges form a clique of size 3 and the other colored
    edges are each cliques of size 1. We can also easily deduct that the maximum
    clique of G is the red clique of size 3.
\end{minipage}
\begin{minipage}{0.5\textwidth}
    \begin{figure}[H]
        \centering
        \begin{tikzpicture}[node distance=2cm]
            \node (1) {1};
            \node (2) at ([shift=(210:2)] 1) {2};
            \node (3) [left of=2] {3};
            \node (4) [above of=3] {4};
            \node (5) [above of=2] {5};
            \node (6) at ([shift=(150:2)] 4) {6};

            \draw[red] (1) -- (2);
            \draw[red] (1) -- (5);
            \draw[green] (2) -- (3);
            \draw[red] (2) -- (5);
            \draw[blue] (3) -- (4);
            \draw[orange] (4) -- (5);
            \draw[cyan] (4) -- (6);
        \end{tikzpicture}
        \caption{Basic graph example}
    \end{figure}
\end{minipage} \\ \\

The MEWC problem can be used to model various types of real-world situations where
the goal is to find a subset of objects with the maximum total weight, and the
objects are connected by weighted edges. Here are a few examples of such situations:

\begin{itemize}
    \item \textbf{Network design}: In a communication network, the MEWC problem
          can be used to find the optimal subset of devices (vertices) to include in
          the network, such that the total cost of communication between the devices
          (edges) is maximum.
    \item \textbf{Protein interaction}: In biology, the MEWC problem can be used
          to find the optimal subset of proteins (vertices) in a protein-protein
          interaction network, such that the total interaction strength (edges)
          between the proteins is maximum.
    \item \textbf{Social network analysis}: In a social network, the MEWC problem
          can be used to find the optimal subset of individuals (vertices) with
          the maximum total relationship strength (edges) between them.
\end{itemize}

% ----- Configuration -----

\subsection{Configuration}

-  Ajouter les configurations que l'on a utilise pour les tests du style la config\\ \\

On this project, we decide to use \textbf{the C++ language} to developp and implement our algorithms. Nevertheless, a debate took place, especially on the choice of the language. We hesitated between Python and C++. The first one was for us easier to handle and was a tool in which we had more confidence in our ability to use it efficiently. The latter was nevertheless preferred because of its speed of execution, which was an important criterion for the study. We did have some problems with memory allocation, which made us regret this choice at times.  \\ \\
To share the code between us, we used \textbf{Github}\footnotemark \footnotetext{\url{https://github.com/sehnryr/Final-Graph-Project-ISEN-CIR3}}. It is a web-based platform for version control, collaboration, and sharing of code, as well as a community of developers who contribute to open source projects and share their knowledge. It was a tool that was difficult for some to get used to quickly, especially on the configuration of the project at home, but which brought us a significant gain in efficiency once we had understood how to use it. To share information and communicate between us, we used \textbf{Discord}.



% ----- Applications -----

\subsection{Example of real-life situations}

As we said, the MEWC has many real-life applications in various fields such as social networks, chemistry, bioinformatics. We could model this problem with some fast example like these :
\begin{itemize}
    \item We can model this problem on social \textbf{social networks}, indeed we can represent each \textbf{users} as a \textbf{vertex} in a graph and add an \textbf{edge} between two vertices if the corresponding individuals \textbf{have some kinds of relationships together}. The weight of the edge could represent \textbf{the degree of relationships} between the two users. The goal here is to identify the group of individuals with the strongest connections within a social network. Some example can be Twitter or Netflix.
    \item Furthermore, we can model the MEWC problem on \textbf{chemistry}, indeed we can represeant each \textbf{chemical compounds} as a \textbf{vertex} in a graph and add an \textbf{edge} between two vertices if the corresponding chemical compounds \textbf{have an intermolecular interaction between them}. The weight of the edge could represent the \textbf{he strength of the corresponding intermolecular interaction}. The goal here is to identify the compound with the strongest intermolecular interactions from a set of potential drug candidates. Some example can be found on research.
\end{itemize}
We will take a practical example which could include and involve ISEN students in our future. We will reuse the presented case to illustrate the different algorithms that we will implement later in the report.\\ \\
\textbf{An example of real-life situations that can be modelled as MEWC} is \ul{the team formation process} during a project, or in the search for a particular social group.
\\ \\
We can imagine that the Student Office of ISEN Nantes is looking to reinforce the video games club of its school. Indeed, the latter has no succession for the following year and is thus led to die if no member presents himself. The future members of the office will have to be in contact with each other during a whole year and it is thus important to find people with common interests so that no tension is formed during their studies. The office has access to the Steam profiles of the students within ISEN (Steam is a video game digital distribution service that gives information about the games played by each one) as well as a record made by the gaming club of the different games played by their members. The fact of playing games in common could bring some people closer, and this makes it a good criterion to create a group that could take over the club because it would share common interests. Otherwise, it would allow to see which games and which group could be present at different events they could organize. Here, forming a team from a group of individuals can be considered as a maximum edge weight clique problem because the goal is to select a subset of individuals such that the members share a common interest.
\\ \\
To model this problem as a maximum edge weight clique problem, we can represent each \textbf{individual} as a \textbf{vertex} in a graph and add an \textbf{edge} between two vertices if the corresponding individuals \textbf{share atleast one game}. The weight of the edge could represent \textbf{the number of game} that they have in common.
\\ \\
For example, on a small scale we could imagine :
\\ \\
\begin{tabular}{|p{0.3\textwidth}|p{0.65\textwidth}|}
    \hline
    \textbf{Students} & \textbf{Game played}                         \\
    \hline
    Youn              & Minecraft, Civilisations, Lost ARK, Among US \\
    \hline
    Martin            & Minecraft                                    \\
    \hline
    Valentin          & Genshin, Minecraft, Civilisations            \\
    \hline
    Bastien           & Genshin, Minecraft, Lost ARK, Among US       \\
    \hline
    Guillaume         & CSGO, Genshin, Overwatch, Stardew Valley     \\
    \hline
    Dorian            & CSGO, Paladins, Overwatch                    \\
    \hline
    Antoine           & League of Legends, Stardew Valley            \\
    \hline
    Thomas            & League of Legends, The Last of US            \\
    \hline
    Alexandre         & League of Legends, Dofus                     \\
    \hline
\end{tabular}
\vspace{1\baselineskip} \\
Which would give us this graph :

\begin{center}
    \begin{tikzcd}
        Youn \arrow[dd, dash, "1"] \arrow[r, dash, "2"] \arrow[ddr, dash, "3"] & Valentin \arrow[r, dash, "1"] \arrow[ddl, dash, "1"] \arrow[dd, dash, "2"] & Guillaume \arrow[ddl, dash, "1"] \arrow[dd, dash, "2"] \arrow[r, dash, "1"] & Antoine \arrow[dd, dash, "1"] \arrow[dr, dash, "1"] \\
        & & & & Alexandre \\
        Martin \arrow[r, dash, "1"] & Bastien & Dorian & Thomas \arrow[ur, dash, "1"]
    \end{tikzcd}
\end{center}

The goal of the maximum edge weight clique problem in this context would be to find a complete subset of individuals such that the sum of the weights of the edges between the individuals is maximized. In this example, the maximum weight clique would be the clique consisting of nodes Youn, Valentin, Martin, Maxence with a total weight of $10(2+1+1+1+3+2)$.

% Indeed, we could imagine that Nils Baussé need to make a team for a robotic event in Nantes during the hollidays. As the students of CIR3 do not all live in Nantes during their vacation period, he needs to form a group that is geographically close to each other so that they can meet quickly, do tests and participate in the event to present the project. Here, forming a team from a group of individuals can be considered as a maximum edge weight clique problem because the goal is to select a subset of individuals in order to optimize the global location of the team.
% \newline

% To model this problem as a maximum edge weight clique problem, you can represent each individual as a node in a graph and add an edge between two nodes if the corresponding individuals are located within 10 km of each other. The weight of the edge could represent a number proportional to the distance between the two people. The closer they are, the bigger the number would be and the further they are, the smaller the number would be. We will take the weight $w$ as : $$w = \frac{1}{\text{distance between the two individuals}} \times 100$$
% \newline

% For example, we could imagine that Youn lives 7km away from Martin, the weigth between these two will be : $$w_{Youn/Martin} = \frac{1}{7} \times 100 = 14.3$$
% \newline
% \begin{center}
%     \begin{tikzcd} 
%         Youn \arrow[dd, dash, "14.3"] \arrow[r, dash, "23"] \arrow[ddr, dash, "43"] & Valentin \arrow[r, dash, "70"] \arrow[ddl, dash, "15"] \arrow[dd, dash, "100"] & Aubin \arrow[ddl, dash, "85"] \arrow[dd, dash, "15"] \arrow[r, dash, "13"] & Antoine \arrow[dd, dash, "12"] \arrow[dr, dash, "10"] \\
%         & & & & Alexandre \\
%         Martin \arrow[r, dash, "16"] & Maxence & Dorian & Thomas \arrow[ur, dash, "12"]
%     \end{tikzcd} 
% \end{center}

% The goal of the maximum edge weight clique problem in this context would be to find a subset of individuals such that the sum of the weights of the edges between the individuals is maximized. In this example, the maximum weight clique would be the clique consisting of nodes Valentin, Aubin, Maxence with a total weight of $255(100+170+85)$.

\newpage