% ----- Fonctionnement -----

\subsection{How it works}

GRASP mainly uses two parts: the first one is the \textbf{greedy randomized heuristic}
and the second one is the \textbf{local search}. The first part is used to
construct the solution and the second one is used to refine it. The algorithm
works by incrementally constructing solutions using greedy randomization. At each
step, the algorithm chooses the next vertex of the clique using a greedy
randomized heuristic. The heuristic is used to decide which vertex should be
added to the current clique in order to maximize the total weight of the clique.
\bigskip

Let $C$ denote the clique to be constructed. GRASP begins with an empty clique $C$.
Let $k=0$, $V_{k=0}=V$ and $E_{k=0}=E$. A plausible greedy choice for the maximum
edge weight clique is to select the vertex with the highest sum of weights of its
adjacent edges with respect to the graph induced by the yet unselected vertices
that are not adjacent to any previously selected vertex. Let $N(v)$ denote the
neighboring vertices of $v$ and $w(u,v)$ denote the weight of the edge between
vertices $u$ and $v$. The greedy choice is to select a vertex with the highest
sum of weight of its adjacent edges. Instead of selecting the greedy choice,
the GRASP construction phase builds a restricted candidate list (RCL) of all
vertices having high sum of adjacent edges weight, but not necessarily the
highest. Let $\Gamma$ be the highest sum of adjacent edges weight in $V_k$, i.e.
\bigskip

$$\Gamma=\max\left\{\sum_{u\in N(v)}w(u,v)|v\in V_k\right\}$$
\bigskip

And let $\alpha>0$ be the restricted candidate parameter. The value restricted
candidate list is:
\bigskip

$$\text{RLC}=\left\{v\in V_k|\sum_{u\in N(v)}w_{uv}>\frac{\Gamma}{1+\alpha}\right\}$$
\bigskip

We next describe a $k$-exchange search procedure in the initial graph $G$. The
idea here is to take as input a clique $C\subseteq V$ of size $p$ and consider
all $k$-tuples of vertices in $C$, for a given parameter $k$, $0<k<p$. For each
$k$-tuple, we consider all possible $k$-tuples $\{v_{i_1},...,v_{i_k}\}$, apply 
an exhaustive search to find a maximum edge weight clique in the graph induced 
by the vertices of $G$ such that $V_k=V\backslash\{v_{i_1},...,v_{i_k}\}$. 
If the resulting clique $\mathcal{N}$ is larger that $C$, the new best solution 
has to be $\mathcal{N}$.
\bigskip

For practical reasons, we use $k=1$ in our implementation.